The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-11 article.tex
Reformatted
Updated Table 2: added missing descriptions and the sdg module (closes #18)

  \begin{itemize}
   \item Perception from 2D coordinates
   \item Perception from 3D coordinates
   \item Wedge assignment
   \item Graph (sub)isomorphism matching
   \item SMARTS matching
   \item Canonicalization
  \end{itemize}

@@

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lp{3cm}p{3cm}l}
  \textbf{Module}            & \textbf{Description}  & \textbf{Major Changes} & \textbf{Dependencies} \\ \hline
  interfaces                 &              & & Vecmath 1.5.2 \\ \hline
  core                       &              & & Google Guava 17.0 \\ \hline % FIXME: how to add https://github.com/google/guava ?
  standard                   &              & & \\ \hline
  render                     &              & Redesigned to make it more modular and support multiple widget toolkits, like AWT and SWT. & \\ \hline
  isomorphism                &              & & \\ \hline
  atomtype                   &              & Unified approach where atom typing is separated from other algorithms. & \\ \hline
  valencycheck               &              & & \\ \hline
  ioformats                  &              & & \\ \hline
  io                         &              & The MDL molfile reader has been rewritten and supports in atom types defind in the specification. & XPP3 1.1.4c \\ \hline
  iordf                      &              & New. & Jena 2.7.4 \\ \hline
  inchi                      &              & & JNI-InChI 0.8~\cite{Spjuth2013}  \\ \hline
  libiocml                   &              & & XOM 1.2.5, CMLXOM 3.1~\cite{Murray-Rust2011} \\ \hline
  smiles                     &              & SMILES support performance and converage is greatly improved. & Beam 0.9.1~\cite{Beam} \\
  smarts                     &              & & Beam 0.9.1~\cite{Beam} \\
  formula                    &              & New. & \\ \hline
  fingerprint                &              & Many new fingerprint types (see text). & Apache Commons Math 3.1.1 \\ \hline
  qsar                       &              & & XOM 1.2.5, JAMA 1.0.3~\cite{Hicklin2012} \\ \hline
  signatures                 &              & & Signatures 1.1 \\ \hline % FIXME: ask Gilleain for the reference
  qsarmolecular              &              & & \\ \hline
  log4j                      &              & & Log4j 1.2.17 \\ \hline
    \end{tabular}
    \end{minipage}

>>>>

  \begin{itemize}
   \item perception from 2D coordinates;
   \item perception from 3D coordinates;
   \item wedge assignment;
   \item graph (sub)isomorphism matching;
   \item SMARTS matching; and
   \item canonicalization.
  \end{itemize}

@@

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lp{3cm}p{3cm}l}
  \textbf{Module}            & \textbf{Description}  & \textbf{Major Changes} & \textbf{Dependencies} \\ \hline
  interfaces                 & Interfaces for the data models. & & Vecmath 1.5.2 \\ \hline
  core                       & Core functionality.             & & Google Guava 17.0 \\ \hline % FIXME: how to add https://github.com/google/guava ?
  standard                   & Common functionality.           & & \\ \hline
  render                     & Graphical rendering.            & Redesigned to make it more modular and support multiple widget toolkits, like AWT and SWT. & \\ \hline
  isomorphism                & Isomorphism and substructure searching. & & \\ \hline
  atomtype                   & Various non-core atom type schemes.     & Unified approach where atom typing is separated from other algorithms. & \\ \hline
  ioformats                  & Definitions of (chemical) input/output formats. & & \\ \hline
  io                         & Readers and writers for input/output formats.  & The MDL molfile reader has been rewritten and supports in atom types defind in the specification. & XPP3 1.1.4c \\ \hline
  iordf                      & Stores data models as in the Resource Description Framework serialization foramts. & New. & Jena 2.7.4 \\ \hline
  inchi                      & IUPAC International Chemical Identifier support. & & JNI-InChI 0.8~\cite{Spjuth2013}  \\ \hline
  libiocml                   & Writer for the Chemical Markup Language format. & & XOM 1.2.5, CMLXOM 3.1~\cite{Murray-Rust2011} \\ \hline
  sdg                        & Structure diagram generation.  & Much improved overlap resolution. & \\ \hline
  smiles                     & Reading and writing in the SMILES format. & SMILES support performance and converage is greatly improved. & Beam 0.9.1~\cite{Beam} \\ \hline
  smarts                     & Substructure searching with the SMARTS format. & & Beam 0.9.1~\cite{Beam} \\ \hline
  formula                    & Chemical formula support. & New. & \\ \hline
  fingerprint                & Calculate fingerprints. & Many new fingerprint types (see text). & Apache Commons Math 3.1.1 \\ \hline
  qsar and qsarmolecular                       & Molecular descriptors.  & & XOM 1.2.5, JAMA 1.0.3~\cite{Hicklin2012} \\ \hline
  signatures                 & Calculation of molecular and atomic signatures. & & Signatures 1.1 \\ \hline % FIXME: ask Gilleain for the reference
    \end{tabular}
    \end{minipage}
